Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-18 vesicle_code/docs/adhesion/adhesion.tex
small changes to paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{In the extensional flow, put a plus sign after the 0.
Indicate the flow with arrows.  Do the same for the shear and Figure 9
(right).}

@@

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
  of vesicle hydrodynamics in an extensional flow.  At a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta=0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  {\em Right}: The definition of the inclination angle.  An inclination
  angle of $\pi$ indicates a doublet whose long axis is parallel to the
  converging direction, while an inclination angle of $\pi/2$ indicates
  a doublet whose short axis is parallel to the converging direction.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.02$.  The doublet tilts to an inclination angle.
  }
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.07$.  The doublet tilts to an inclination angle.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.1$.  The vesicles extensional rate has overcome the adhesive force,
  and the vesicles doublet is broken.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta0.4$, extensional rate is $\chi =
  0.1$.  Initially, the doublet tilts to an inclination angle, and then
  the extensional rate overcomes the adhesive force and the doublet is
  broken.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the Hamaker constant is $H=0.7$,
  the adhesion length scale is $\delta = 0.4$, and the shear rate is
  $\chi=0.5$.}
  \todo[inline]{Superimpose the background velocity on the leftmost plot
  to indicate the shearing motion}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[htp]
  \begin{minipage}{0.6\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/angleDefinition.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram} {\em Left}:Phase diagram
  of vesicle hydrodynamics in an extensional flow.  At a fixed Hamaker
  constant $H=0.7$ and adhesion length scale $\delta=0.4$.  For small
  extensional rates, the doublet structure is not broken (blue marks),
  while at large extensional rates, the doublet is broken (red marks).
  {\em Right}: The definition of the inclination angle.  An inclination
  angle of $\pi$ indicates a doublet whose long axis is parallel to the
  converging direction, while an inclination angle of $\pi/2$ indicates
  a doublet whose short axis is parallel to the converging direction.
  The square mark is a stagnation point while the round point is located
  at the center of the vesicle.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.02$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.07$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.1$.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.19\textwidth,trim={5cm 2cm 5cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the Hamaker constant is $H = 0.7$, and the
  adhesion length scale is $\delta = 0.4$, extensional rate is $\chi =
  0.1$.  Initially, the doublet tilts to an inclination angle, and then
  the extensional rate overcomes the adhesive force and the doublet is
  broken.  The center of the vesicle, denoted with a black square, is a
  stagnation point.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the Hamaker constant is $H=0.7$,
  the adhesion length scale is $\delta = 0.4$, and the shear rate is
  $\chi=0.5$.}
  \todo[inline]{Superimpose the background velocity on the leftmost plot
  to indicate the shearing motion}
\end{figure}
\todo[inline]{Indicate the shear flow in the right most plot.}
